%%
%% Author: mirco
%% 19.06.18
%%

% Preamble
\documentclass[11pt,aspectratio=169]{beamer}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{tabularx,booktabs}
\usetheme{Copenhagen}
\usecolortheme{crane}
\usepackage[autostyle]{csquotes}

\setbeamertemplate{section page}
{
\begin{centering}
    \begin{beamercolorbox}[sep=12pt,center]{part title}
        \usebeamerfont{section title}\insertsection\par
    \end{beamercolorbox}
\end{centering}
}


\title{Comparative Argument Mining}
\author{Mirco Franzek}
\date{June 26, 2018}
\begin{document}
    \maketitle

    \section{Introduction}
    \frame{\sectionpage}

    \begin{frame}
        \frametitle{Comparative Argument Mining: An example}
        Given a sentence and two comparable objects like

        \begin{center}
            \LARGE \emph{Toyota} is better than \emph{BMW} at\ldots providing reliable, economical auto transport.
        \end{center}

        Decide if

        \begin{enumerate}
            \item the sentence compares Toyota and BMW
            \item Toyota wins the comparison or
            \item BMW wins the comparison
        \end{enumerate}

    \end{frame}

    \begin{frame}
        \frametitle{Possible Applications}

        \begin{itemize}
            \item Online comparison portals like \url{Check24.de}
            \item Sentiment Mining
            \item Languange Understanding
        \end{itemize}

    \end{frame}


    \begin{frame}
        \frametitle{Related Work}

    \end{frame}


    \section{Creating a data set}
    \frame{\sectionpage}
    \subsection{Data Source}
    \begin{frame}
        \frametitle{Common Crawl}
        \begin{itemize}
            \item CommonCrawl\footnote{\url{http://commoncrawl.org}} is a freely accessible data set of crawled websites
            \item A preprocessed version\footnote{\cite{Panchenko:2017aa}} was used
            \begin{itemize}
                \item English content only (?)
                \item HTML was removed
                \item Splitted into sentences
                \item Duplicates were removed
            \end{itemize}
            \item 3,288,963,864 unique sentences; inserted into an Elasticsearch index
            \item 428,932 sentences contain \emph{is better than}
        \end{itemize}

    \end{frame}

    \begin{frame}
        \frametitle{Domains}
        \begin{itemize}
            \item Comparable object pairs are needed
            \item Goal: Cover a wide range of different objects
            \item \emph{Computer Science}: operating systems, abstract concepts, software, \ldots
            \item \emph{Brands}: cars, food, electronics, \ldots
            \item \emph{Random}: book authors, soccer teams, universities, \ldots

        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Obtaining objects}
        \begin{itemize}
            \item Computer Science and Brands: \emph{List of \ldots} pages from Wikipedia were used to select suitable objects
            \item Random
            \begin{itemize}
                \item 25 seed words were randomly selected (cork, Hamster, Florida, ninja\ldots)
                \item JoBimText\footnote{http://ltmaggie.informatik.uni-hamburg.de/jobimtext/} was used to find the 10 most similar words for each seed word
            \end{itemize}
            \item Each object was checked against a frequency dictionary, words with a frequency of were removed
            \item For each object type (Wikipedia source page or seed word), all possible combinations were created.
        \end{itemize}

    \end{frame}

    \begin{frame}
      \frametitle{Pairs: Examples}

      \begin{tabularx}{\textwidth}{XXX}
          \toprule
          Brands & Computer Science & Random \\
          \midrule
          Microsoft vs. Apple & Java vs. Python & baseball vs. hockey \\
          Nikon vs. Leica & Eclipse vs. Netbeans & fishing vs. swimming\\
          Coca-Cola vs. Pepsi & OpenGL vs. Direct3D & SUV vs. minivan\\
          Nike vs. Adidas & Integer vs. Float & Kennedy vs. Nixon\\
          Ibuprofen vs. Advil & USB vs. Bluetooth & plastic vs. wood\\
          Ford vs. Honda & Oracle vs. MysQL & Harvard vs. Princeton\\

          \bottomrule

      \end{tabularx}

    \end{frame}

    \begin{frame}
        \frametitle{Sentence Sampling}

        \begin{itemize}
            \item 21 words (like better, worse, slower, inferior, cooler) were selected as comparison cue words
            \item for 90 percent of the pairs, the index was queried for sentences containing both objects and one cue word
            \item for the remaining 10 percent, the cue word was omitted
            \item 2500 sentences for each domain were randomly sampled from the result
        \end{itemize}

    \end{frame}
    
    \begin{frame}
      \frametitle{Sentence Sampling: Examples}
        \begin{itemize}
            \item \enquote{There is no doubt \textbf{Python} is better than \textbf{Ruby} at in aspect you will pick.}
            \item \enquote{Goodnight \textbf{NetBeans}, Hello \textbf{Eclipse}}
            \item \enquote{\textbf{stone} is harder than \textbf{metal}}
            \item \enquote{arrrggghh...\textbf{Python} is a terrible language - only \textbf{Perl} sucks worse.}
            \item \enquote{Good to see again a \textbf{Renault} ahead of a \textbf{Ferrari}.}
        \end{itemize}
    \end{frame}

    \subsection{Crowdsourcing}
    \begin{frame}
        \frametitle{Setup}

    \end{frame}

    \begin{frame}
        \frametitle{Results: Brands}

    \end{frame}

    \begin{frame}
        \frametitle{Results: Computer Science}

    \end{frame}

    \begin{frame}
        \frametitle{Results: Random}

    \end{frame}


    \begin{frame}
        \frametitle{Results: All}

    \end{frame}

    \section{Classification}
    \frame{\sectionpage}
    \subsection{Setup}
    \begin{frame}
        \frametitle{Algorithms}

    \end{frame}

    \begin{frame}
        \frametitle{Evaluation}

    \end{frame}

    \begin{frame}
        \frametitle{Baseline}

    \end{frame}

    \subsection{Features}
    \begin{frame}
        \frametitle{Sentence Embeddings}

    \end{frame}

    \begin{frame}
        \frametitle{LexNet: Dependency Path I}

    \end{frame}


    \begin{frame}
        \frametitle{LexNet: Dependency Path II}

    \end{frame}

    \begin{frame}
        \frametitle{Other features}

    \end{frame}

    \subsection{Training Results}

    \begin{frame}
        \frametitle{Three classes}

    \end{frame}


    \begin{frame}
        \frametitle{Binary}

    \end{frame}


    \section{Discussion and Future Work}
    \frame{\sectionpage}
    \begin{frame}
        \frametitle{abc}

    \end{frame}

\end{document}